Individual heterogeneity in the functional network topography of medial prefrontal

### 2019-09-03 Manuscript.Rmd
further cleaning of the structural code

# update Summaries dfs
curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries[[1]]$Vertex]})
for (i in seq(nSubj)) {
  Summaries[[i]]$Curvature <- curvData[[i]]
}

# select vmPFC like Lopez-Persem

>>>>

# select vmPFC like Lopez-Persem
# select bilateral parcels that cover the mask seen in fig. 4B in Lopez-Persem et al. 2019
# the parcels surrounding sulci ROS-S and SU-ROS are: a24, p32, s32, 10r
persemROI <- c("_25_", "_s32_", "_a24_", "_10v_", "_10r_", "_p32_", "_OFC_")
primarySulci <- c("L_a24_ROI", "R_a24_ROI", "L_s32_ROI", "R_s32_ROI", "L_p32_ROI", "R_p32_ROI", "L_10r_ROI", "R_10r_ROI")

indx <- getCoords(Labels = persemROI, Coords = Summaries[[1]])$Index
vmpfc <- rep(0, nVertices)
vmpfc[indx] <- 1

# update Summaries dfs, and reduce to vmPFC only
curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries[[1]]$Vertex]})
for (i in seq(nSubj)) {
  Summaries[[i]]$Curvature <- curvData[[i]]
  Summaries[[i]]$SubjID <- subjList[[i]]
  Summaries[[i]]$vmpfc <- vmpfc
  Summaries[[i]] <- Summaries[[i]] %>% mutate(region = case_when(
    y < 0 ~ "PCC",
    vmpfc == 1 ~ "vmPFC",
    TRUE ~ "dmPFC"
  ),
  sulcus = ifelse(Curvature < 0, 1, 0))
}

# # mimic the binning and averaging L-P did on vmPFC
# # this will plot a similar figure for a similar mask, plus a more dorsal mPFC one and PCC
# do.call(rbind, Summaries) %>%
#   mutate(Curvature = round(Curvature, digits = 1)) %>%
#   filter(Curvature > -0.5) %>%
#   group_by(SubjID, region, FiedlerBinary, Curvature) %>%
#   summarise(mFV = mean(FiedlerVec)) %>%
#   group_by(region, FiedlerBinary, Curvature) %>%
#   summarise(meanFV = mean(mFV),
#             seFV = sd(mFV, na.rm = T) / sqrt(100)) %>%
#   ggplot(aes(Curvature, meanFV, color = region, linetype = as.character(FiedlerBinary))) +
#     geom_line(size = 1.2, show.legend = F) +
#     labs(y = "Mean Fiedler Vector Value", color = "Region") +
#     geom_errorbar(aes(Curvature, ymin = meanFV - seFV, ymax = meanFV + seFV), width = 0.08, size = 1.2, linetype = "solid", show.legend = F) +
#     scale_x_continuous(breaks = c(-0.4, 0, 0.4, 0.8)) +
#     geom_point(size = 2) +
#     scale_color_manual(values = c("firebrick", "dodgerblue4", "gold2")) +
#     geom_vline(xintercept = 0, linetype = "dashed") +
#     geom_hline(yintercept = 0, linetype = "dashed") +
#     theme(#legend.position = c(0.9, 0.32),
#           legend.key=element_blank(),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_blank(),
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 22))

# MIXED EFFECTS LOGISTIC ESTIMATING SULCUS FROM FV AND REGION, WORKS BUT CHANGE REFERENCE
sulcData <- do.call(rbind, Summaries) %>%
  mutate(Curvature = round(Curvature, digits = 1),
         region = factor(region, levels = list("vmPFC", "dmPFC", "PCC"))) #%>%
  #filter(abs(FiedlerVec) > 0.01)

sulcGLM <- list()
sulcGLM$vmpfc <- glmer(FiedlerBinary ~ Curvature * region + (1 | SubjID), data = sulcData, family = "binomial")
sulcData$region <- factor(sulcData$region, levels = list("dmPFC", "vmPFC", "PCC"))
sulcGLM$dmpfc <- glmer(FiedlerBinary ~ Curvature * region + (1 | SubjID), data = sulcData, family = "binomial")

# right now it looks like vmpfc FV is negatively related to curvature, but the opposite is true for dmPFC
lapply(sulcGLM, summary)
